---
title: "Reproducible Research With R"
author: "Nicholas Good - Environmental & Radiological Health Sciences - CSU"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# What is reproducible research?

## Reproducible versus Replicable?

## Why creating reproducible work is important - Integrity

## Why creating reproducible work is important - Usability

## Why creating reproducible work is important - Sanity

# Towards making your research reproducible

## Coding style

## Version control

## Code sharing

## Markup

# R tools for reproducible research

## RStudio projects

## R Markdown

## Git / GitHub integration

# Applications: Exploratory data analysis

# Applications: Presentations

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

